---
title: "trafford-tweet-dash"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: rows
    logo: logo.png
    css: styles.css
---

<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.10.1/css/all.css" crossorigin="anonymous">

```{r setup, include=FALSE}
library(shiny) ; library(flexdashboard) ; library(tidyverse) ; library(rtweet) ; library(tidytext) ; library(reshape2) ; library(igraph) ; library(grid) ; library(ggraph) ; library(lubridate) ; library(DT) ; library(htmltools) ; library(scales) ; library(emo) ; library(knitr) ; library(kableExtra)

twitter_token <- readRDS("twitter_token.rds")
```

``````{r reactive}
tweets <- eventReactive(input$submit,{
    if(is.null(input$query)){
      return()
    }
    
    results <- search_tweets(q = input$query, 
                  n = 500,
                  include_rts = FALSE,
                  `-filter` = "replies",
                  lang = "en",
                  token = twitter_token)
    filter(results, !screen_name %in% c("TraffordCouncil", "OneTrafford", "TPAction", "AndrewHWestern", "Saratodd16"))
  })

words <- reactive({
  tweets() %>%
    mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
           text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
           text = str_remove_all(text, "[^\x01-\x7F]")) %>% 
    unnest_tokens(word, text, token = "tweets") %>%
    filter(!word %in% stop_words$word,
           !word %in% str_remove_all(stop_words$word, "'"),
           str_detect(word, "[a-z]"),
           !str_detect(word, "^#"),
           !str_detect(word, "@\\S+")) %>% 
    select(word)
})

message <- reactive({
  HTML(paste0("<strong>", nrow(tweets()), " </strong> tweets (excluding retweets and replies) were retrieved between ", strftime(min(tweets()$created_at), '%R on %A %d %B %Y', tz = 'GMT'), " and ", strftime(max(tweets()$created_at), '%R on %A %d %B %Y', tz = 'GMT'), "."))
})
```

Sidebar {.sidebar}
=====================================

```{r}
radioButtons("query", label = h5("Choose a topic:"),
                c("Trafford Council" = "@TraffordCouncil OR \"Trafford Council\"",
                  "OneTrafford" = "@OneTrafford OR \"One Trafford\"",
                  "#ClimateEmergency",
                  "COVID-19" = "Trafford OR \"Old Trafford\" OR \"Trafford Park\" OR \"Gorse Hill\" OR Firswood OR Davyhulme OR Flixton OR Stretford OR Urmston OR \"Sale Moor\" OR \"Ashton upon Mersey\" OR Partington OR Broadheath OR Timperley OR Altrincham OR \"Hale Barns\" OR Bowdon AND coronavirus OR #coronavirus OR #CoronavirusOutbreak OR COVID19 OR COVID-19 OR #COVID19 OR #COVIDー19 OR #Corvid19uk"))
actionButton("submit", "Submit query", 
    style = "color: #fff; background-color: #969696; border-color: #737373")
```

<br />

```{r, period}
uiOutput("message")

output$message <- renderUI({
  message()
})
```

Tweets {data-icon="fab fa-twitter"}
=======================================================================

```{r table}
DTOutput("table")

mention_url <- function(x) {
  x %>%
    stringr::str_split(" ") %>%
    purrr::flatten_chr() %>%
    str_c("<a href='https://twitter.com/", ., "' target='_blank'>@", ., "</a>") %>%
    stringr::str_c(collapse = " ")
}

hashtag_url <- function(x) {
  x %>%
    stringr::str_split(" ") %>%
    purrr::flatten_chr() %>%
    str_c("<a href='https://twitter.com/search?q=%23", ., "' target='_blank'>#", ., "</a>") %>%
    stringr::str_c(collapse = " ")
}

output$table <- renderDT({
    tweets() %>%
    select(created_at, screen_name, text, hashtags, mentions_screen_name, urls_expanded_url, urls_t.co, retweet_count, favorite_count) %>% 
      mutate(created_at = strftime(created_at, '%F %T', tz = 'GMT'),
             screen_name = paste0("<a href='https://twitter.com/", screen_name, "' target='_blank'>@", screen_name, "</a>"),
             hashtags = ifelse(
               !is.na(hashtags),
               map_chr(hashtags, hashtag_url),
               ""),
             mentions_screen_name = ifelse(
               !is.na(mentions_screen_name),
               map_chr(mentions_screen_name, mention_url),
               ""),
             urls_expanded_url = ifelse(is.na(urls_expanded_url), "", paste0("<a href='", urls_expanded_url, "'target='_blank'>", urls_t.co, "</a>"))) %>%
    select(-urls_t.co) %>% 
      datatable(
        fillContainer = TRUE,
        width = "100%", 
        rownames = FALSE, 
        escape = FALSE,
        options = list(
          search = list(regex = TRUE),
          searchHighlight = TRUE,
          scrollX = TRUE, 
          autoWidth = TRUE,
          columnDefs = list(
            list(className = 'dt-left', targets = "_all"))
          ), 
        colnames = c("Timestamp", "Handle", "Tweet", "Hashtags", "Mentions", "URL", "RTs", "Likes")
      )
  })
```

Charts {data-icon="fas fa-chart-bar"}
=======================================================================

Row
-----------------------------------------------------------------------

### Timeline of activity
```{r}
plotOutput("timeline")

output$timeline <- renderPlot({
  ts_plot(tweets(), "hours") +
    geom_hline(yintercept = 0, size = 1, colour = "#333333") +
    geom_line(colour = "#2C5E80", size = 1) +
    scale_y_continuous(expand = c(0.005, 0.005)) +
    labs(x = NULL, y = NULL, title = NULL, subtitle = NULL,
         caption = "Data collected from Twitter's REST API via rtweet") +
    theme_minimal(base_size = 16) +
    theme(plot.margin = unit(rep(0.5, 4), "cm"),
          panel.grid.major.x = element_blank(),
          panel.grid.minor = element_blank(),
          plot.caption = element_text(margin = margin(t = 15)))
})
```

### Top tweeters
```{r}
plotOutput("tweeters")

output$tweeters <- renderPlot({
  tweets() %>% 
    count(screen_name, sort = TRUE) %>%
    filter(n > 1) %>% 
    top_n(10) %>%
    mutate(screen_name = paste0("@", screen_name)) %>% 
    ggplot(aes(fct_reorder(screen_name, n, .desc = TRUE), n)) +
    geom_col(fill = "#2C5E80") +
    geom_text(aes(label = n), hjust = 1.5, vjust = 0.5, colour = "white", fontface = "bold") +
    geom_hline(yintercept = 0, size = 1, colour = "#333333") +
    scale_y_continuous(expand = c(0.005, 0.005)) +
    labs(x = NULL, y = NULL, title = NULL, subtitle = NULL,
         caption = "Data collected from Twitter's REST API via rtweet") +
    coord_flip() +
    guides(fill = FALSE) +
    theme_minimal(base_size = 16) +
    theme(plot.margin = unit(rep(0.5, 4), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          plot.caption = element_text(margin = margin(t = 15)),
          axis.text.x = element_blank())
})
```

Row
-----------------------------------------------------------------------

### Most used hashtags
```{r}
plotOutput("hashtags")

output$hashtags <- renderPlot({
  tweets() %>% 
    unnest_tokens(hashtag, text, "tweets", to_lower = FALSE) %>%
    filter(str_detect(hashtag, "^#")) %>%
    count(hashtag, sort = TRUE) %>%
    filter(n > 1) %>% 
    top_n(10) %>% 
    mutate(hashtag = factor(hashtag, levels = hashtag)) %>% 
    ggplot(aes(reorder(hashtag, n), n)) +
    geom_segment(aes(x = hashtag, xend = hashtag, y = 0, yend = n), 
                 linetype = "dotted", colour = "#212121", size = 0.5) +
    geom_point(colour = "#2C5E80", size = 10) +
    geom_text(aes(label = comma(n, accuracy = 1)), fontface = "bold", colour = "white") +
    labs(x = NULL, y = NULL, title = NULL, subtitle = NULL,
         caption = "Data collected from Twitter's REST API via rtweet") +
    coord_flip() +
    theme_minimal(base_size = 16) +
    theme(plot.margin = unit(rep(0.5, 4), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_text(hjust = 0))
})
```

### Most used emoji
```{r}
htmlOutput("emoji")

output$emoji <- renderText({
  tweets() %>%
    mutate(emoji = ji_extract_all(text)) %>%
    unnest(cols = c(emoji)) %>%
    count(emoji, sort = TRUE) %>%
    top_n(5) %>% 
    kable(col.names = NULL) %>%
    kable_styling(
      font_size = 20,
      bootstrap_options = c("hover"), position = "left") 
})
```

Analysis {data-icon="fas fa-brain"}
=======================================================================

Row
-----------------------------------------------------------------------

### Most common positive and negative words
```{r}
plotOutput("sentiment")

output$sentiment <- renderPlot({
  words() %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(sentiment = str_to_title(sentiment)) %>% 
    count(word, sentiment, sort = TRUE) %>%
    ungroup() %>% 
    group_by(sentiment) %>%
    filter(n > 1) %>% 
    top_n(10) %>%
    ggplot(aes(reorder(word, n), n, fill = sentiment)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = n), hjust = 1.5, vjust = 0.5, colour = "white", fontface = "bold") +
    scale_fill_manual(values = c("#767676", "#F3A641")) +
    labs(x = NULL, y = NULL, title = NULL, subtitle = NULL,
         caption = "Data collected from Twitter's REST API via rtweet") +
    facet_wrap(~sentiment, scales = "free_y") +
    coord_flip() +
    theme_minimal(base_size = 16) +
    theme(plot.margin = unit(rep(0.5, 4), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          plot.caption = element_text(margin = margin(t = 15)),
          strip.text = element_text(face = "bold", hjust = 0.1),
          axis.text.x = element_blank())
}) 
```

Row
-----------------------------------------------------------------------

### Most commonly associated words
```{r}
plotOutput("network")

output$network <- renderPlot({
  bigram_graph <- tweets() %>%
    mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
           text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
           text = str_remove_all(text, "[^\x01-\x7F]")) %>%
    unnest_tokens(word, text, token = "tweets") %>%
    filter(!word %in% stop_words$word,
           !word %in% str_remove_all(stop_words$word, "'"),
           str_detect(word, "[a-z]"),
           !str_detect(word, "#\\S+"), 
           !str_detect(word, "@\\S+")) %>%
    select(word) %>%
    unnest_tokens(bigram, word, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    count(word1, word2, sort = TRUE) %>%
    select(word1, word2, n) %>%
    filter(n > 2) %>% 
    graph_from_data_frame()
  
  ggraph(bigram_graph, layout = "fr") +
    geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    labs(x = NULL, y = NULL, title = NULL, subtitle = NULL,
         caption = "Data collected from Twitter's REST API via rtweet") +
    theme_void(base_size = 16) +
    theme(plot.margin = unit(rep(0.5, 4), "cm"),
          plot.caption = element_text(margin = margin(t = 15)))
}) 
```

About {data-icon="fa-info-circle"}
=====================================

```{r}
includeMarkdown("about.md")
```
